### 2023-05-22 letters/response-ref-1-v1.tex

To address the time-complexity of maximizing the log-likelihood, we use Lemma 3.1 (now 4.1).  The complexity of logistic regression with $n$ observations and covariates of dimension $d$ is $O(nd)$; so we can view maximizing the true likelihood as subsampling with a very high rate so that the design-unbiased score functions have minimal approximation error in comparison to to directly maximizing the likelihood function.  Under this assumption, at the final stage we have the relative complexity of $(4 \times 60 \times \tau_i) \cdot n \cdot d$ compared to the expected time-complexity under subsampling with rate $c$ per minute of $(c \times \tau_i) \cdot n \cdot d$.  In practice, this can lead to large differences in run time; specifically, under a 4Hz sensor the time-complexity of the maximum likelihood estimate at its observation frequency will take approximately $2^{13}$ times as long as subsampling at a rate of once every half-hour.  In our first example, using the average run times at each sampling rate to project run time at four times per second yields an approximately 2.0 hour run time. In our second example, we project a run time at four times per second of 6.2 hours. In both instances, the relative efficiency gain would be negligible suggesting a huge computational increase for minimal relative information gain. We now make this point abundantly clear by amending Section 5 with Remark 5.1 to include time complexity discussion.

\vspace{5mm}

\item {\it How about using a concurrent model for $h_i (t;\theta) = h_0 (t; \theta) \exp (g_t (H_{i,t}^N)^\top \alpha + x_i (t) \beta (t))$. This does not look at the past window like the suggested model but this drawback might be compensated with the constructed features $g_t (H_{i,t}^N)$ that capture the past. The concurrent approach might be much less expensive computationally. This can be added as an alternative to the simulations.}

\vspace{5mm}
The above calculations hold for even the concurrent model, so that approach is still computationally expensive. We discuss this futher in Remark 5.1 where we show the computation trade-off.  We find the approach computationally demanding with minimal information gain.
\vspace{5mm}

@@

\item {\it In section 5.2.1 what is uncongeniality? Does it have a mathematical
meaning?}

\vspace{5mm}
Rubin defined conditions for an imputation procedure to be so-called ‘proper’ for a given complete data analysis. If in addition the complete data analysis gives frequentist valid inferences, MI using Rubin’s rules yields valid frequentist inferences. Meng defined the concept of congeniality between an imputation procedure and an analyst’s complete (and incomplete) analysis procedure. The imputation model and the analyst’s complete data procedure are said to be congenial if there exists a unifying Bayesian model which embeds the imputer’s imputation model and the analyst’s complete data procedure.  A formal definition of congeniality can be found Bartlett and Hughes (2020).  If an imputation and analysis procedure are congenial, this implies the imputation is proper for the analysis procedure. Meng showed that for certain types of uncongeniality, Rubin’s variance estimator is conservative, ensuring the intervals have at least the advertised coverage level. In other settings, however, it can be biased downwards, leading to under-coverage of confidence intervals.  We provide these details as part of our discussion in Section 6.2.1.
\vspace{5mm}

\item {\it Page 23, Figure 2. EDA seems to spike at the end. Even AI seems to be turning up. Add longer history to both the Figures.}
\vspace{5mm}

We have investigated this issue and there is a slight uptick in EDA but not in ACC; however, we are concerned that showing a longer history may not be helpful given our focus on a potentially shorter $\Delta$ based on the data analysis.  Therefore, we keep the plot as is, and note that there is a spike at 30-minutes for EDA while emphasizing that most of the signal appears in the 15-minute range.  This helps motivate our data adaptive choice of $\Delta$ in Section 7.1 which confirms that $\Delta = 15$ is the most appropriate choice although results are consistent across a range of $\Delta$ choices.
\vspace{5mm}

@@

\item {\it Doesn’t Figure 3 suggest smaller $\Delta$?}

\vspace{5mm}
We agree.  We have re-run the analysis with a window length of 15 minutes.  A comparison of AIC provides empirical evidence that the smaller $\Delta$ was an appropriate choice.  We now present $\Delta = 15$ in the main paper, and then $\Delta =5$ and $30$ as a sensitivity analysis.
\vspace{5mm}

@@

\item {\it What features were constructed for the real data analysis?}

\vspace{5mm}
As the case study was meant to be illustrative, we controlled for time-of-day by restricting to 9AM to 8PM as users who were asleep cannot press the button and thus were not 'at-risk'.  We now include the number of button presses in the prior 12 hours as another feature to control for the heterogeneity. This is clarified in Section 7.1.
\vspace{5mm}

@@

\begin{enumerate}
\item {\it There exists a good amount of recent efforts modeling event data with functional data predictor or joint modeling, so a literature review on relevant papers would be useful. See, for example, papers by Dr. Ciprian Crainiceanu from Johns Hopkins, Dr. Sheng Luo from Duke, and Dr. Jiguo Cao from Simon Fraser.}

\vspace{5mm}
We have added a detailed discussion of related work in Section 1.1, which includes the specific suggestions on relevant works provided by the second referee; specifically, we discuss recent modeling of time-to-event data with functional covariates as well as joint modelling from a functional regression perspective.  We contrast these approaches with our design-based approach which becomes necessary when considering high-frequency sensor processes rather than traditional longitudinal studies as the number of measurement occasions increase from tens to thousands/millions of times per individual.  We connect and contrast our use of subsampling with the general use of subsampling in handling massive data and its recent use in massive data with functional predictors.
\vspace{5mm}

\item {\it It might be worth mentioning existing literature on historical functional linear models, e.g., papers by Dr. Damla Senturk from UCLA and collaborators.}

\vspace{5mm}
We now state that our proposed joint model includes a recent history functional linear model which we now link with the previous work by Damla Senturk and others.  This motivates Section 5.2 which provides additional empirical study and discussion of the tuning parameter~$\Delta$.
We added Section 1.1 to describe the related work and connect our methodology to the existing literature.
\vspace{5mm}

@@

\item {\it As with any recent history functional linear models, the size of the window ($\Delta$) is an important parameter. So it would be helpful to see some efforts on developing a data-adaptive method for the selection of $\Delta$.}

\vspace{5mm}
We agree.  As with other tuning parameters, we take an AIC approach to selection of $\Delta$ in order to be data-adaptive.  We study the performance of this criteria as part of the simulation study in Section 5.2 and then apply it in the case study to determine the appropriate window-length.
\vspace{5mm}

@@

\item {\it While in Section 3.6 the paper discusses penalized functional regression to reduce overfitting, it is unclear if the paper actually adopts it in simulation studies and application. It is of interest how the smoothing parameter is selected. My concern is that if no penalty is employed, with more than 30 basis functions, overfitting can be severe and much wider confidence bands are often obtained}

\vspace{5mm}
We now clarify that throughout the simulation studies and application we employ the penalization procedure to reduce overfitting.  We have found that without careful tuning of the penalty parameter, the overfitting can be severe as stated by the referee.
\vspace{5mm}

\item {\it In the theoretical section, it would be helpful to understand what intermediate results Assumption 3.4 will lead to.}

\vspace{5mm}
To address this and the Referee \#1's comment, we have added Remark 4.5 to clarify settings where Assumption 3.4 will hold. Specifically, if the functional process is bounded, i.e., $|X(t,s)| < M$ and the other component is also bounded then we are guaranteed to have these assumptions hold.  This is likely to be true in most practical settings and thus demonstrates the reasonableness of our assumptions for applied settings.
\vspace{5mm}

@@

\item {\it In the simulation study, it would make sense to me consider a coefficient function for which the magnitude is not only decaying further away from current time and also becomes 0 at $t-\Delta$. In addition, it might be helpful to use relative errors to quantify the accuracy of estimation of coefficient functions.}

\vspace{5mm}
By design, $\beta(s) = 0$ for $s > \Delta$.  Therefore, we considered two settings for~$\beta(s)$. First, an exponential decaying $\beta(s)$ that mimics a weighted averaging over past values that decays to $0$ smoothly as $s \to^- \Delta$. Second, a sinusoidal $\beta(s)$ that mimics taking a temporal difference over two average windows but is different from $0$ near $s =\Delta$.   We clarify these choices in Section 5. To address the other comment, we have added a row to Table 2 that reports relative MISE (RMISE).
\vspace{5mm}

@@

\item {\it Section 2.1 discusses the rationale of modeling functional predictor without noises. Note that the proposed methodology is actually suitable for data with noises. First, the data application seems to suggest noises are indeed present; see Figure 2 (A). Second, I am not sure I fully understand why in the equation after (3), the conditional probability is conditioning on functional predictor observed up to censoring or truncation time. Isn’t it more sensible to condition on functional predictor observed up to t? Then, the conditional probability will not depend on functional predictor beyond time t.}

\vspace{5mm}
We have decided that the point we were trying to raise is not essential to the main manuscript, so we have moved the discussion of \emph{independent evolution} and its implication that $\varepsilon (t) = 0$ for all $t >0$ to the Appendix.  The key issue we were trying to clarify is that the traditional joint model formulation in which the observed health process and time-to-event are conditionally independent given the latent process implies that the hazard function conditional on the entire observed health process depends on values after the current time.  In the case study, for example, this implies that the expected risk of a button press given the entire sensor process will depend on future activity index and electrodermal activity.  This holds unless we assume the measurement error is set to zero.  The referee is correct that we will only compute conditional probabilities given the historical functional predictor; however, the likelihood factorization means that we implicitly are defining a conditional intensity given the entire functional predictor and the traditional approach has this undesirable dependence. While the author still thinks it an important point that he wishes was more well appreciated in the joint modeling literature, the current paper has enough content for this discussion to be omitted from the main manuscript.  Moreover, the empirical impact seems to be limited and therefore it is better to make this point in the Appendix.
\vspace{5mm}

@@

\item {\it In Section 3.1, the paper considers modeling the mean function separately at event times and non-event times. Is there some reasoning or justification for this?}

\vspace{5mm}
Since the event times~$T_i$ depend heavily on the event intensity function~$h_i (t;\theta)$ while the subsampling times~$D_i$ depend on the subsampling intensity function~$\pi_i(t)$, we chose to model the mean and covariance functions separately to ensure good approximation when applying the spectral decomposition of the estimated covariance function.  Given the potential difference between the distributions, we choose to model the mean and covariance functions separately to ensure good approximation when applying the spectral decomposition of the estimated covariance function.  To illustrate this, Figure 2 in Appendix D.3 presents mean curves for EDA and AI over the same 30 minute window. Another reason for treating these two distinctly is that the missing data imputation from Petrovich et al. (2018) requires distinct covariance functions.
\vspace{5mm}
